Optimal (Multiway) Spatial Joins

### 2024-05-29 4.2.tex
4.2

\noindent \underline{\em Proof of Statement (2).} 
First, we deviate a little to prove the following statement. For any rectangle $r\in \bigcup_{i = 1}^{k-2}$, if a segment $h\in H$ crosses $r$, then $h$ also crosses the trimmed rectangle of $r$, denoted as $r'$. Since the x-range of $r'$ is a subset of the x-range of $r$, it suffices to show that the y-coordinate of $h$ is in the range $[\ybot(r'), \ytop(r')]$. Since $\ybot(r')$ is the y-coordinate of the lowest segment in $H$ that crosses $r$, and $h$ crosses $r$, we have $\ybot(r') \leq \ybot(h)$. Moreover, since $\ytop(r')$ is the y-coordinate of the highest segment in $H$ that crosses $r$, and $h$ crosses $r$, we have $\ytop(h) \leq \ytop(r')$. Therefore, $h$ crosses $r'$. We can prove that if a segment $v\in V$ crosses $r$, then $v$ also crosses the trimmed rectangle of $r$ analogously.

>>>>

\noindent \underline{\em Proof of Statement (2).} 
First, we deviate a little to prove the following statement. For any rectangle $r\in \bigcup_{i = 1}^{k-2}$, if a segment $h\in H$ crosses $r$, then $h$ also crosses the trimmed rectangle of $r$, denoted as $r'$. Since the x-range of $r'$ is a subset of the x-range of $r$, it suffices to show that the y-coordinate of $h$ is in the range $[\ybot(r'), \ytop(r')]$. Let $h = [x_1,x_2]\times y$. Since $\ybot(r')$ is the y-coordinate of the lowest segment in $H$ that crosses $r$, and $h$ crosses $r$, we have $\ybot(r') \leq y$. Moreover, since $\ytop(r')$ is the y-coordinate of the highest segment in $H$ that crosses $r$, and $h$ crosses $r$, we have $y \leq \ytop(r')$. Therefore, $y \in [\ybot(r'), \ytop(r')]$ and $h$ crosses $r'$.  Analogously, we can prove that if a segment $v\in V$ crosses $r$, then $v$ also crosses the trimmed rectangle of $r$.
